CES analysis for Paul Brockway rebound paper

### 2015-09-10 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now doing resampling in Rebound paper.

# Tell whether to re-run the analysis to create the models.
# This file will use previously-saved models to generate
# the paper if set to FALSE, greatly reducing time.
# If something changes in the data or in the code that
# performs the analysis, set 
# rerunModels = TRUE
# once to re-generate the information needed to 
# create the paper.
# ********************************************************
rerunModels=FALSE
# ********************************************************
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE
)
@

@@

<<Models>>=
fileName <- file.path("models", "Brockway2015Models.rds")
if (!rerunModels){
  # load from the file on disk
  models <- readRDS(fileName)
} else {
  # re-run the models and save to disk.
  # In RStudio, be sure to set the working directory to the source file directory.
  models <- lapply(countries, function(coun){
    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
  })
  names(models) <- countries
  # Save the models.
  saveRDS(models, file = fileName)
}
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

# Tell whether to re-run the analysis to create the models.
# This file will use previously-saved models to generate
# the paper if set to FALSE, greatly reducing time.
# If something changes in the data or in the code that
# performs the analysis, set 
# rerunModels = TRUE
# once to re-generate the information needed to 
# create the paper.
# ********************************************************
rerunModels=FALSE
rerunResamples=FALSE
nResamples <- 100 # Number of resamples
# ********************************************************
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE
)
@

@@

<<Models>>=
modelsFileName <- file.path("models", "Brockway2015Models.rds")
if (!rerunModels){
  # load from the file on disk
  models <- readRDS(modelsFileName)
} else {
  # re-run the models and save to disk.
  # In RStudio, be sure to set the working directory to the source file directory.
  models <- lapply(countries, function(coun){
    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
  })
  names(models) <- countries
  # Save the models.
  saveRDS(models, file = modelsFileName)
}
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resampling Calculations}
\label{sec:resampling_calculations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<Resampling>>=
resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
if (!rerunResamples){
  # load resample data from the file on disk
    resampleCoeffs <- readRDS(resampleFileName)
} else {
  # Run resampling on models.
  resampleCoeffs <- leaf_apply(l = models, class = c("cesModel", "plm"), f = function(mod, mod_name){
    resampledFits(mod, method = "wild", n = nResamples)$coeffs %>%
      mutate(
        Country = mod_name
      )
  }) %>% bind_rows
  saveRDS(resampleCoeffs, file = resampleFileName)
}
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model Results}
\label{sec:model_results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resampling Results}
\label{sec:resampling_results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Calculate rebound by Equation~\ref{eq:rebound}.
%
\begin{equation} \label{eq:rebound}
  Re \approx 1 - \frac{\rho}{1 + \rho} = \sigma_{(kl)e}\; .
\end{equation}
%
<<calc_rebound>>=
# Add a Rebound column to the resample coefficients
resampleCoeffs <- resampleCoeffs %>%
  # Applying the approximation Re ~ 1 - rho/(1 + rho) = sigma
  mutate(Re = sigma) 
@
%
Plot resampling results for \Sexpr{nResamples} resamples in Figure~\ref{fig:rebound_graph}.
%
<<rebound_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$\\alpha_e$ vs. $Re$ for all three countries.">>=
standardScatterPlot(data=resampleCoeffs, mapping=aes(Re, alpha_3), facet_formula=~Country, alpha=0.2, orig_color = "black") +
    # scale_x_continuous(limits=c(0, 5)) + 
    scale_x_log10(limits = c(0.001,100), breaks = c(0.01, 0.1, 1, 10), labels = c(0.01, 0.1, 1, 10)) +

    scale_y_continuous(breaks=c(seq(0, 1, 0.2))) +
    geom_vline(xintercept = 1, colour="gray50", size=0.1) +
    labs(y=expression(alpha[e]))
@
